### 2023-04-18 paper.Rmd
figure caption

```{r, fig.cap = "The relationship between the objectives $\\mathit{SSE}$ and $\\mathit{SSE_{Var}}$ across all ways to partition $N = 14$ normally distributed random values into $K = 2$ groups. The partition represented by the square maximizes $\\mathit{SSE}$ and thus minimizes the difference in means between groups; the partition represented by the triangular maximizes $\\mathit{SSE_{Var}}$ and thus minimizes the difference in variances between groups. The partition represented by the diamond maximizes $\\mathit{SSE_{kplus}}$ and satisfies both constituting criteria to an almost optimal degree.", fig.height = 5, fig.width = 5}

>>>>

```{r, fig.cap = "The relationship between the objectives $\\mathit{SSE}$ and $\\mathit{SSE_{Var}}$ across all ways to partition $N = 14$ normally distributed random values into $K = 2$ groups. The partition represented by the square maximizes $\\mathit{SSE}$ and thus minimizes the difference in means between groups; the partition represented by the triangular maximizes $\\mathit{SSE_{Var}}$. The partition represented by the diamond maximizes $\\mathit{SSE_{kplus}}$ for $w_1 = w_2 = 1$, and satisfies both constituting criteria to an almost optimal degree.", fig.height = 5, fig.width = 5}
